Memory Safety: A Systematic Literature Review

### 2024-03-13 paper.tex
Working on defining research questions

\documentclass[sigconf]{acmart}

@@

The 1995 movie Hackers~\cite{Wikipedia_contributors2024-zr} prescient predictions regarding the ease
of breaking into computing systems in cyberspace have came to fruition. The White House Office of
the National Cyber Director (ONCD) released a report calling for the technical community to
proactively reduce the attach surface in cyberspace with a two pronged approach. First we need to
address the root cause of many of the most heinous cyber attacks, memory unsafe programming
languages~\cite{United_States_Gov2024-pp}. Second, we need to establish better cybersecurity quality
metrics so we can have a better understanding of the cyber security landscape.

@@

This Systematic Literature Review aims to provide a comprehensive and up-to-date analysis of the
existing body of research surrounding memory safety. By systematically reviewing and synthesizing
the wealth of knowledge accumulated in this field, we seek to uncover the current state of
understanding, identify emerging trends, and highlight gaps in our knowledge that warrant further
investigation.

@@

For our research methodolgy we ~\cite{Stuart2007-cc}

@@

@@

\begin{itemize}
    \item RQ1:
    \item RQ2:
    \item RQ3:
\end{itemize}

@@

>>>>

\documentclass[sigconf]{acmart}
\usepackage{listings, listings-rust}
\usepackage{xcolor}

\NewDocumentCommand{\codeword}{v}{%
\texttt{\textcolor{blue}{#1}}
}

\lstset{language=Rust, keywordstyle={\bfseries \color{blue}}}

@@

The 1995 movie Hackers~\cite{Wikipedia_contributors2024-zr} prescient predictions regarding the ease
of breaking into computing systems in cyberspace have came to fruition. The White House Office of
the National Cyber Director (ONCD) released a report calling for the technical community to
proactively reduce the attack surface in cyberspace with a two pronged approach. First we need to
address the root cause of many of the most heinous cyber attacks, memory unsafe programming
languages~\cite{United_States_Gov2024-pp}. Second, we need to establish better cybersecurity quality
metrics so we can have a better understanding of the cyber security landscape.

@@

This Systematic Literature Review (SLR) aims to provide a comprehensive and up-to-date analysis of
the existing body of research surrounding memory safety. By systematically reviewing and
synthesizing the wealth of knowledge accumulated in this field, we seek to uncover the current state
of understanding, identify emerging trends, and highlight gaps in our knowledge that warrant further
investigation.

@@

For our research methodolgy we followed the advice of Kitchenham and Charters~\cite{Stuart2007-cc}
and divided our review into the 3 discrete phases, planning the review, conducting the review, and
reporting the review results.

@@

Before we start researching we must first confirm the need for a SLR. The recent report released by
ONCD~\cite{United_States_Gov2024-pp} has conveniently done this job for us by compiling a report
detailing the need for research in the domain of memory safety. Thus, we must first define the most
important aspect of the planning phase, the research questions.

@@

\begin{itemize}
    \item \textbf{RQ1:} How can \lstinline{unsafe} Rust derived from C be converted to safe Rust?
    \item \textbf{RQ2:} How can we build Rust bindings into core abstractions?
    \item \textbf{RQ3:} How can we better find vulnerabilities in \lstinline{unsafe} blocks
\end{itemize}

@@

In this section we address the proposed research questions.
